---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# OTN Workshop targets

This branch is an exercise in converting the workflows outlined in the living [OTN workshop materials](https://ocean-tracking-network.github.io/otn-workshop-base/) to [`targets`](https://docs.ropensci.org/targets/).

Pull requests are welcomed by anyone and everyone!

## To get started

  1.    Clone this repository and switch to the `otn-workshop-targets` branch
  2.    Open the `_targets.R` file
  3.    Open up the  [OTN workshop page](https://ocean-tracking-network.github.io/otn-workshop-base/) and select an episode
  4.    Pick a chunk of code or an example
        a.    if it's short, assign it directly to a target in the `_targets.R` file
        b.    if it's long, wrap it in a function within the episode's `.R` file in the `episodes/` directory
  5.    Save `_targets.R`, run `targets::tar_make()`, and watch what happens!
  6.    Run `tar_objects()` to see what was created
  7.    Run `tar_read(some_object_name)` to look at a specific target
  8.    Commit and push your changes
  9.    Open a pull request!


## Completion

  -   [X] Setup/Background
  -   [ ] Intro to R
      -   [X] Setting up R
      -   [X] Operators
      -   [X] Functions
      -   [ ] Vectors and Data Types
      -   [ ] Indexing and Subsetting
      -   [ ] Missing Data
  -   [ ] Starting with Data Frames
  -   [ ] Intro to Plotting
  -   [ ] Telemetry Reports - Imports
  -   [ ] Telemetry Reports for Array Operators
  -   [ ] Telemetry Reports for Tag Owners
  -   [ ] Introduction to glatos Data Processing Package
  -   [ ] More features of glatos
  -   [ ] Basic Visualization and Plotting
  -   [ ] Introduction to actel
  -   [ ] Preparing ACT/OTN/GLATOS Data for actel
  -   [ ] Basic Animation
  -   [ ] Animation with pathroutr
  -   [ ] Quality Control Checks with Remora
  -   [ ] Spatial and Temporal Modelling with GAMs
  -   [ ] Introduction to the miscYAPS package
  -   [ ] Introduction to Git for Code
  -   [ ] Other OTN Telemetry Curricula

## Current network
```{r, results='asis', echo=FALSE}
cat(
  '```mermaid\n',
  targets::tar_mermaid(),
  '\n```',
  sep = '\n'
)
```

